CASE DETECTION OF TUBERCULOSIS PATIENTS USING MACHINE-LEARNING

### 2024-04-08 products/manuscript/Manuscript.qmd
part4_2

These results highlight the potential of advanced machine learning algorithms, particularly Random Forest, in enhancing TB diagnosis and early detection strategies, offering valuable insights for clinical decision-making and the development of more effective screening protocols.
{{< pagebreak >}}

>>>>

The results highlight the potential of advanced machine learning algorithms, particularly Random Forest, in enhancing TB diagnosis and early detection strategies, offering valuable insights for clinical decision-making and the development of more effective screening protocols.
{{< pagebreak >}}
